A Survey of Real-Time Strategy Game AI\\ Research and Competition in StarCraft

### 2013-03-08 survey.tex

\section{Introduction}\label{sec:intro}
\IEEEPARstart{S}{ince} Michael Buro's call for research in real-time strategy (RTS) games \cite{Buro03rts}, many researchers have answered the call. Specially, AI competitions like the ``AIIDE StarCraft AI Competition'' have caused many AI techniques to be
applied to RTS AI. We will list and classify these approaches, explain their 
power and their downsides and conclude on what is left to achieve human-level 
RTS AI.

Many  challenging AI  problems can  be found  in  dynamic environments
where  one does  not have  a  perfect, complete  information of  their
current  state, as well  as their  evolution.  Road  traffic, finance,
weather  forecasts are  examples of  huge, complex,  real-life dynamic
environments. RTS games can be seen as a simplification of a real-life
environment, where there  exist simpler rules in a  finite and smaller
world, but are complex enough  to bring very difficult and interesting
problems  to  the scientific  community,  like  decision making  under
uncertainty  or  real-time adversarial planning.   Finding  efficient  techniques
to address these problems  on  RTS  games can  thus  profit broader  AI
domains, but  have also concrete  and direct applications in  the huge
industry of  video games.
%,  generating worldwide two  and a  half times more revenue than the Film industry in 2011.
% This statement is not fair, the reference I found it only compare all the game industry revenue (including hardware sales) vs theatrical film industry revenue (i.e. not DVD sales, ...)

This paper, aiming to provide a one-stop guide on what is the state of
the art in RTS AI, and with a particular emphasis on the work done in StarCraft. 
It is organized as follows: Section~\ref{sec:rts}
introduces real-time strategy games, in particular the game StarCraft,
and  the main  AI challenges  in RTS  games.  Section~\ref{sec:review}
reviews  the existing  work on  RTS games  tackling  these challenges.
Section~\ref{sec:bot} shows  the current state  of the art of bots, i.e. a computer-controlled players, 
for  StarCraft, presenting  seven bots participating  to annual
StarCraft    AI    competitions     for    a    couple    of    years.
Section~\ref{sec:competition}  presents these two  annual competitions
held  at the AIIDE  and CIG  conferences and a StarCraft bot game ladder\footnote{An extended tournament, which can potentially go on indefinitely.}.  Section~\ref{sec:questions}
compiles open questions  in RTS game AI which must  be tackled to make
bots reaching a high human-level play.
% skip "empirical evidence..." for the moment
Finally, the paper concludes on discussions and perspectives.

@@

%\begin{IEEEbiography}[{\includegraphics[width=2cm, keepaspectratio]{figures/santi.jpg}}]{Santiago Onta\~{n}\'{o}n}
\begin{IEEEbiographynophoto}{Santiago Onta\~{n}\'{o}n}
is an assistant professor in the Computer Science Department at Drexel University. His main research interests are game AI, case-based reasoning and machine learning, fields in which he has published more than 90 peer-reviewed papers. He obtained his PhD form the Autonomous University of Barcelona (UAB), Spain. Before joining Drexel University, he held postdoctoral research positions at the Artificial Intelligence Research Institute (IIIA) in Barcelona, Spain, at the Georgia Institute of Technology (GeorgiaTech) in Atlanta, USA, and at the University of Barcelona, Spain.  
\end{IEEEbiographynophoto}

>>>>

\section{Introduction}\label{sec:intro}
\IEEEPARstart{T}{he} field of real-time strategy (RTS) game AI has advanced significantly since Michael Buto's call for research in this area \cite{Buro03rts}. Specially, competitions like the ``AIIDE StarCraft AI Competition'' have motivated the exploration of many AI approaches in the context of RTS AI. We will list and classify these approaches, explain their 
strengths and weaknesses and conclude on what is left to achieve human-level 
RTS AI.

Complex dynamic environments, where it is not possible to have perfect nor complete information about the current state or about the dynamics of the environment, pose significant challenges for artificial intelligence. Road  traffic, finance, or
weather  forecasts are  examples of such large, complex, real-life dynamic
environments. RTS games can be seen as a simplification of a real-life
environment, with simpler dynamics in a  finite and smaller
world, although still complex enough  to bring very difficult and interesting
problems  to  the scientific  community like  decision making  under
uncertainty  or  real-time adversarial planning. Finding efficient  techniques for
tackling  these problems  on  RTS  games can  thus  benefit broader  AI
domains, but  also have concrete  and direct applications in  the ever growing
industry of  video games.%, generating worldwide two  and a  half times more revenue than the Film industry in 2011.
% This statement is not fair, the reference I found it only compare all the game industry revenue (including hardware sales) vs theatrical film industry revenue (i.e. not DVD sales, ...)

This paper, aiming to provide a one-stop guide on what is the state of
the art in RTS AI, and with a particular emphasis on the work done in StarCraft. 
It is organized as follows: Section~\ref{sec:rts}
introduces real-time strategy games, in particular the game StarCraft,
and  the main  AI challenges  in RTS  games.  Section~\ref{sec:review}
reviews  the existing  work on tackling these challenges in RTS games.
Section~\ref{sec:bot} analyzes several current state of the art RTS game playing agents (called {\em bots}), selected form the participants to annual
StarCraft    AI    competitions.
Section~\ref{sec:competition}  presents results of the recent annual competitions
held at the AIIDE  and CIG conferences and a StarCraft bot game ladder\footnote{An extended tournament, which can potentially go on indefinitely.}.  Section~\ref{sec:questions}
compiles open questions in RTS game AI. Finally, the paper concludes on discussions and perspectives.

@@

%\begin{IEEEbiography}[{\includegraphics[width=2cm, keepaspectratio]{figures/santi.jpg}}]{Santiago Onta\~{n}\'{o}n}

\begin{IEEEbiographynophoto}{Santiago Onta\~{n}\'{o}n}
is an assistant professor in the Computer Science Department at Drexel University. His main research interests are game AI, case-based reasoning and machine learning, fields in which he has published more than 90 peer-reviewed papers. He obtained his PhD form the Autonomous University of Barcelona (UAB), Spain. Before joining Drexel University, he held postdoctoral research positions at the Artificial Intelligence Research Institute (IIIA) in Barcelona, Spain, at the Georgia Institute of Technology (GeorgiaTech) in Atlanta, USA, and at the University of Barcelona, Spain.  
\end{IEEEbiographynophoto}
